---
title: "Data Report"
author: "JOSEPH HARRY MENSAH"
date: "2022-11-08"
output: 
  powerpoint_presentation: 
    toc: yes
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(tidyverse)
library(readxl)
library(janitor)
library("gridExtra")

survey <- read_excel("Questionaire.xlsx")
```

## Question: The training session was useful to my work 

## The training session was useful to my work

```{r cars, echo=FALSE, dpi=500}
attended_similar <- (subset(survey, survey$`Have you attended any training of this sort before?`== "Yes"))
similar_training <- ggplot(attended_similar, aes(College, `The training session was useful to my work`, fill=Designation)) +
  geom_bar(stat="identity", position = "dodge", width = 0.5)  + scale_fill_hue(l=60) +
  labs(title ="Perpective: Respondent attended similar training",
       subtitle="",
       caption ="Source:Refresher Training Survey, University of Cape Coast") +
  ylab(" ")
similar_training

```

## The training session was useful to my work

```{r pressure, echo=FALSE, dpi=500}
not_attended_similar <- (subset(survey, survey$`Have you attended any training of this sort before?`== "No"))
no_similar_training <- ggplot(not_attended_similar, aes(College, `The training session was useful to my work`, fill=Designation)) +
  geom_bar(stat="identity", position = "dodge", width = 0.5) + scale_fill_hue(l=60) +
  labs(subtitle="Perspective: Respondent has not attended similar training",
       caption = "Source: August 2022 Refresher Training Survey, University of Cape Coast") +
  ylab("")
no_similar_training
```

## Comparison: The training session was useful to my work

```{r dream, echo=FALSE, dpi=500}

grid.arrange(similar_training, no_similar_training, nrow = 2, ncol=1)
```

## Question: The training will impact positively on my work
## Positive Impact On Work
```{r dream2, echo=FALSE, dpi=500}
similar_training_impact <- ggplot(attended_similar, aes(College, `The training will impact positively on my work `, fill=Designation)) +
  geom_bar(stat="identity", position = "dodge", width = 0.5) +
  labs(title="The training will impact positively on my work",
       subtitle="Perspective: Respondent attended similar training") +
  ylab("")
similar_training_impact
```

## Positive Impact On Work
```{r dream3, echo=FALSE, dpi=500}
no_similar_training_impact <- ggplot(not_attended_similar, aes(College, `The training will impact positively on my work `, fill=Designation)) +
  geom_bar(stat="identity", position = "dodge", width = 0.9) +
  labs(title = "The training will impact positively on my work",
    subtitle="Perspective: Respondent has not attended similar training",
       caption = "Source: August 2022 Refresher Training Survey, University of Cape Coast") +
  ylab("")
no_similar_training_impact
```

## Comparison: The training will impact positively on my work 
```{r summary1, echo=FALSE, dpi=500}
grid.arrange(similar_training_impact, no_similar_training_impact, nrow = 2, ncol=1)
```

##  Question: I need such training regularly
## The need for such training regularly
```{r dream5, echo=FALSE, dpi=500}
similar_and_regular_training <- ggplot(attended_similar, aes(College,`I need such training regularly `, fill=Designation)) +
  geom_bar(stat="identity", position = "dodge", width = 0.5) +
  labs(title="I need such training regularly",
       subtitle="Perspective: Respondent attended Similar training") +
  ylab("")
similar_and_regular_training
```

## The need for such training regularly
```{r dreams6, echo=FALSE, dpi=500}
no_similar_and_regular_training <- ggplot(not_attended_similar, aes(College,`I need such training regularly `, fill=Designation)) +
  geom_bar(stat="identity", position = "dodge", width = 0.8) +
  labs(subtitle="Perspective: Respondent has not attended Similar training",
       caption = "Source: August 2022 Refresher Training Survey, University of Cape Coast") +
  ylab("")
no_similar_and_regular_training
```

## Comaparison: I need such training regularly
```{r echo=FALSE, dpi=500}
grid.arrange(similar_and_regular_training, no_similar_and_regular_training, nrow = 2, ncol=1)
```

## Question : I have acquired the basic knowledge necessary to use the UCCOSIS
## Acquired basic Knowledge on UCCOSIS usage
```{r echo=FALSE, dpi=500}
acquired_basic_knowledge1 <- ggplot(attended_similar, aes(College,`I have acquired the basic knowledge necessary to use the UCCOSIS  `, fill=Designation)) +
  geom_bar(stat="identity", position = "dodge", width = 0.4) +
  labs(title="I have acquired the basic knowledge necessary to use the UCCOSIS",
       subtitle="Perspective: Respondent attended Similar training") +
  ylab("")

acquired_basic_knowledge1
```

## Acquired basic Knowledge on UCCOSIS usage
```{r echo=FALSE, dpi=500}
acquired_basic_knowledge2 <- ggplot(not_attended_similar, aes(College,`I have acquired the basic knowledge necessary to use the UCCOSIS  `, fill=Designation)) +
  geom_bar(stat="identity", position = "dodge", width = 0.8) +
  labs(subtitle="Perspective: Respondent has not attended Similar training",
       caption = "Source: August 2022 Refresher Training Survey, University of Cape Coast")+
  ylab("")
acquired_basic_knowledge2
```

## Comparison: I have acquired the basic knowledge necessary to use the UCCOSIS 
```{r echo=FALSE, dpi=500}
grid.arrange(acquired_basic_knowledge1, acquired_basic_knowledge2, nrow = 2, ncol=1)
```

## Question: I need a user manual for the UCCOSIS
## The Need For A User Manual
```{r echo=FALSE, dpi=500}
needs_user_manual_1 <- ggplot(attended_similar, aes(College,`I need a user manual for the UCCOSIS `, fill=Designation)) +
  geom_bar(stat="identity", position = "dodge", width = 0.4) +
  labs(title="I need a user manual for the UCCOSIS",
       subtitle="Perspective: Respondent attended Similar training")+
  ylab("")
needs_user_manual_1
```

## The Need For A User Manual
```{r echo=FALSE, dpi=500}
needs_User_manual_2 <- ggplot(not_attended_similar, aes(College,`I need a user manual for the UCCOSIS `, fill=Designation)) +
  geom_bar(stat="identity", position = "dodge", width = 0.8) +
  labs(subtitle="Perpective: Respondent has not attended Similar training",
       caption = "Source: August 2022 Refresher Training Survey, University of Cape Coast")+
  ylab("")
needs_User_manual_2
```

## Comparison: I need a user manual for the UCCOSIS
```{r echo=FALSE, dpi=500}
grid.arrange(needs_user_manual_1, needs_User_manual_2, nrow = 2, ncol=1)
```
